---
title: "Analysis"
author: "Patrick Halbach, Johannes Nakayama"
date: "27 8 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(magrittr)
library(arrow)
library(igraph)
```

```{r}
df <- arrow::read_feather(
  file.path("experiments", "grid_sc0", "agents", "adata.feather")
)
```

```{r}
graph <- igraph::read_graph(
  file.path("experiments", "grid_sc0", "graphs", "rep_01.gml"),
  format = "gml"
)
```

```{r}
gsize(graph)
```

```{r}
df$TickNr %<>% as.numeric()
df$AgentID %<>% as.factor()
df$StubbornCount %<>% as.numeric()
df$GridHeight %<>% as.numeric()
df$Replicate %<>% as.numeric()
df$Culture %<>% as.factor()
```

```{r unique-cultures}
df %>% 
  filter(Replicate == 1) %>% 
  filter(TickNr == max(TickNr)) %>% 
  select(Culture) %>%
  unique() %>% 
  # summarize(UniqueCultures = n()) %>% 
  identity()
```

```{r seperate-components}
components(graph)$no
```


```{r}

```


## Measurements

independent:
  * stubborn count [numeric]
  * network type [factor]: 
    * ("grid", "barabasi-albert", "watts-strogatz-0.05", "watts-strogatz-0.10", "watts-strogatz-0.15", "watts-strogatz-0.20")

dependent:
  * unique cultures [numeric]
  * seperate components [numeric]
  * size of biggest component [numeric]
  * distribution of dimension values / excess zeros: simulated value - expected value (number of dimension values divided by 10) [numeric]
  




